---
title: "ST_DA_exercise"
author: "Rajiv Kumar"
date: "Tuesday, January 13, 2016"
output: word_document
---
###Background:

1. ~700k rows of ranking data (App_ID Country Date Hour Device Rank)
2. ~ 3.5k rows of download data (App_ID Country Date Device Downloads)

The rank of an app for a given (country, date, hour, device) combination represents its position in an ordered list of app_ids associated with the combination.

For example, in USA, on 5/13/14 at 20:00:00 hours, the apps on iPhone top free charts had the following order [454, 1549, 2171]. App 454 was rank 1, app 1549 was rank 2 and app 2171 was rank 3.
 
We'd like you to try and answer the following questions for these data sets (below):
```{r echo=FALSE}
options(warn=-1)
options(message=FALSE)
options(tidy=TRUE)
options(fig.height=12)
options(fig.width=12)

suppressMessages(library(ggplot2)) # To draw Plots
suppressMessages(library(tidyr))   # To wrangle our data, if required
suppressMessages(library(dplyr))  # To wrangle our data,if required
library(lubridate)
```


##Question#1:What are your initial observations about the ranking and download datasets?

###Answer: 

First of all lets load the data sets.

```{r}
#read the given download info csv file


df_parsed_log <- read.csv(file= file.path("E:","OPT/JobSearch/Assesment/dataset.csv"))
df_parsed_log$read<-!is.na(df_parsed_log$status)
str(df_parsed_log)
op <- options(digits.secs=6)
options(op)

df_parsed_log$sent_month<-month(strptime(df_parsed_log$send_time,'%Y-%m-%d %H:%M:%OS'),label=TRUE)

df_parsed_log$read_month<-month(as.Date(df_parsed_log$Read_at,format='%d/%b/%Y:%H:%M:%S'),label=TRUE)



head(df_parsed_log)
str(df_parsed_log)


df_parsed_log_by_media<-df_parsed_log %>% group_by(MediaType) %>% summarise(Total_read=sum(read=='TRUE',na.rm=TRUE))
head(df_parsed_log_by_media)
df_parsed_log_by_media_top10<-head(arrange(df_parsed_log_by_media,desc(Total_read)),10)
# Top 10 most popular media type
ggplot(aes(x=MediaType,y=Total_read),data=arrange(df_parsed_log_by_media_top10,Total_read))+geom_bar(stat="identity")+
        theme(axis.text.x=element_text(angle=90, hjust=1))
`````
Lets see the distribution of populare media types each month
```{r}
df_parsed_log_by_media_month<-df_parsed_log %>% group_by(MediaType,read_month) %>% summarise(Total_read=sum(read=='TRUE',na.rm=TRUE))
tail(df_parsed_log)
df_parsed_log_by_media_month_top10<-head(arrange(df_parsed_log_by_media_month,desc(Total_read,na.rm=TRUE)),30)

ggplot(aes(x=MediaType,y=Total_read),data=subset(df_parsed_log_by_media_month_top10,Total_read>0))+geom_bar(stat="identity")+
        facet_wrap(~read_month)+
        theme(axis.text.x=element_text(angle=90, hjust=1))


```

Lets see the distribution by article type
```{r}
df_parsed_log_by_topic<-df_parsed_log %>% group_by(Topic) %>% summarise(Total_read=sum(read=='TRUE',na.rm=TRUE))
tail(df_parsed_log)
df_parsed_log_by_Topic_top10<-head(arrange(df_parsed_log_by_topic,desc(Total_read,na.rm=TRUE)),10)

ggplot(aes(x=Topic,y=Total_read),data=subset(df_parsed_log_by_Topic_top10,Total_read>0))+geom_bar(stat="identity")+
        theme(axis.text.x=element_text(angle=90, hjust=1))
```



```{r}
str(df_parsed_log)
df_parsed_log_by_topic_month_rnr<-df_parsed_log %>% group_by(Topic) %>% summarise(Total_read=sum(read=='TRUE',na.rm=TRUE),Total_not_read=sum(read=='FALSE',na.rm=TRUE))
tail(df_parsed_log_by_topic_month_rnr)
df_parsed_log_by_Topic_month_top10_rnr<-head(arrange(df_parsed_log_by_topic_month_rnr,desc(Total_read,na.rm=TRUE)),10)

ggplot(aes(x=Topic,y=Total_read),data=subset(df_parsed_log_by_Topic_month_top10_rnr,Total_read>0))+geom_bar(stat="identity")+
        
        theme(axis.text.x=element_text(angle=90,hjust=1))

```


```{r}
df_parsed_log_by_topic_month<-df_parsed_log %>% group_by(Topic,read_month) %>% summarise(Total_read=sum(read=='TRUE',na.rm=TRUE))
tail(df_parsed_log)
df_parsed_log_by_topic_month<-df_parsed_log_by_topic_month[df_parsed_log_by_topic_month$Total_read>0,]
library(plyr)

df_parsed_log_by_Topic_month_top10<-head(arrange(df_parsed_log_by_topic_month,desc(Total_read)),30)


df_parsed_log_by_Topic_month_top10<-(arrange(df_parsed_log_by_topic_month,desc(Total_read)))


df_parsed_log_by_Topic_month_top10<-bind_rows(head(arrange(subset(df_parsed_log_by_topic_month,read_month=='Jan'),desc(Total_read)),10),
head(arrange(subset(df_parsed_log_by_topic_month,read_month=='Feb'),desc(Total_read)),10),
head(arrange(subset(df_parsed_log_by_topic_month,read_month=='Mar'),desc(Total_read)),10))
View(df_parsed_log_by_Topic_month_top10)

articles_read<-ggplot(aes(x=Topic,y=Total_read),data=subset(df_parsed_log_by_Topic_month_top10,Total_read>0))+geom_bar(stat="identity")+
        facet_wrap(~read_month)+
        theme(axis.text.x=element_text(angle=90,hjust=1))

```

Lets see how many articles of each type were sent
```{r}
detach("package:plyr", unload=TRUE) 
library(plyr)
df_parsed_log_by_topicsent_month<-df_parsed_log %>% group_by(Topic,sent_month) %>% summarise(Total_sent=n())


df_parsed_log_by_topicsent_month_top10<-bind_rows(head(arrange(subset(df_parsed_log_by_topicsent_month,sent_month=='Jan'),desc(Total_sent)),10),
head(arrange(subset(df_parsed_log_by_topicsent_month,sent_month=='Feb'),desc(Total_sent)),10) ,
head(arrange(subset(df_parsed_log_by_topicsent_month,sent_month=='Mar'),desc(Total_sent)),10))


View(df_parsed_log_by_topicsent_month_top10)
article_sent<-ggplot(aes(x=Topic,y=Total_sent),data=df_parsed_log_by_topicsent_month_top10)+geom_bar(stat="identity")+
        facet_wrap(~sent_month)+
        theme(axis.text.x=element_text(angle=90,hjust=1))

```

Arrange the plots to get better idea.

```{r}
require(gridExtra)
grid.arrange(articles_read,article_sent,nrow=2)
```
 in order to calculate the percentage, lets inner join these two data sets
 
 
```{r}
df_inner_joined<-(inner_join(df_parsed_log_by_topicsent_month_top10,df_parsed_log_by_Topic_month_top10,by=c("Topic","sent_month"="read_month")))
```

```{r}
df_inner_joined$likelihood<-df_inner_joined$Total_read / df_inner_joined$Total_sent

View(df_inner_joined)
```
Lets draw the likelihoods
```{r}
ggplot(aes(x=Topic,y=likelihood),data=df_inner_joined)+
        geom_bar(stat="identity")+
        facet_wrap(~sent_month)+
        theme(axis.text.x=element_text(angle=90,hjust=1))

```



